### 2023-09-25 main.tex
fixed

\paragraph{Proof of formula \eqref{exactCorrelations}} Consider $m$ particles of non-empty types $s_{i}\in\{1,\ldots,N-1\}$ in positions $y_{i}\in\{1,\ldots,L\}$ for all $i=1,\ldots,m$. We aim to compute the non-equilibrium stationary state correlation $\langle n_{s_{1}}^{y_{1}}\cdots n_{s_{m}}^{y_{m}} \rangle_{stat}$. By using duality, we showed in \eqref{CorrelationByABS-prob} that

@@

The two points correlations with respect the non equilibrium distribution of the occupation variable of the species $s_{1},s_{2}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ with $x_{1}< x_{2}$ reads 

@@

Therefore, we obtain the second cumulant, i.e. the two-point connected correlation as 

@@

The three points correlations with respect the non equilibrium distribution of the occupation variable of the species $s_{1},s_{2},s_{3}\in \{1,\ldots,N-1\}$ at coordinates $y_{1},y_{2},y_{3}\in \{1,\ldots,L\}$ such that $y_{1}<y_{2}<y_{3}$

@@

Therefore, we obtain the third cumulant, i.e. the three-point connected correlation as 

@@

As a consequence, using this sequence of transformations we can find all the eigenvectors of $H$ from the ones of $H_{0}$. Moreover, this allows to retrieve the steady state of $H$, by applying the sequence of transformation to the vacuum state, i.e. a state where all the sites are empty. This last transformation $W$ is non-local and requires a joint work of perturbation theory and integrability, via the Quantum Inverse Scattering Method (QISM), to be constructed. 

@@

The above matrices satisfy:

@@

	M_{0}(x)=R_{01}(x)\ldots R_{0L}(x)\qquad \widehat{M}_{0}=R_{0L}(x)\ldots R_{01}(x)
$U_{0}(x)$ satisfies the following exchange relation

@@

Using the matrix form of $U_{0}(x)$ written in \eqref{matrixForm-U}, the transfer matrix $T(x)$ reads

@@

Arguing similarly we write the elements of $U_{0}(x)$  as polynomials in $x$ 

@@

We will need the charge expansion of $T(x)$. As it will be clear in the following, only the first three coefficients for the diagonal elements of $U_{0}(x)$ and only the first one for the non-diagonal elements of $U_{0}(x)$ will be needed. Therefore, using \eqref{RURU}, we compute: 

@@

\item For $D_{i,j}(x)$ with $i,j=2,\ldots,N$ such that $i\neq j$
\begin{equation}\label{Dij-Charge}
D_{i,j}^{2L}=-2e_{ji}^{tot}
\end{equation}
\end{itemize}
\textbf{Remark}: when restricted to the case of 2 species, we obtain equations (2.24)-(2.30) of \cite{frassek2020eigenstates}. \\ \\
Using these polynomial expansions we write the first three conserved charges of the system

\begin{align}
Q^{2L+2}&=D_{N,N}^{2L+1}-\sum_{i=1}^{N-1}D_{ii}^{2L+1}=N
\end{align}
\begin{align}
Q^{2L+1}&=ND_{N,N}^{2L+1}+A^{2L}-\sum_{i=1}^{N-1}D_{ii}^{2L}=N+2L-1
\end{align}
\begin{align}
Q^{2L\phantom{+}}&=ND_{N,N}^{2L}+D_{N,N}^{2L-1}-\sum_{i=1}^{N-1}D_{ii}^{2L-1}+\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
\end{align}
The charges $Q^{2L+2}$ and $Q^{2L+1}$ are proportional to the identity matrix, while $Q^{2L}$ contains non diagonal matrices and the boundary parameters $\alpha_{i},\beta_{i}$ $\forall i=1,\ldots,N-1$.\\
By construction it follows that 
\begin{equation}
\left[Q^{2L},H^{''}\right]=Q^{2L}H^{''}-H^{''}Q^{2L}=0
\end{equation}
while the commutation with the Hamiltonian $H^{''}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. We introduce the following matrix:
\begin{equation}
Q^{2L}_{0}:=ND_{N,N}^{2L}+D_{N,N}^{2L-1}-\sum_{i=1}^{N-1}D_{ii}^{2L-1}
\end{equation}
that is, using the coefficients previously computed, 
\begin{equation}\label{Q0Exp}
\begin{split}
Q^{2L}_{0}=(N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}
\end{split}
\end{equation}

We also introduce 
\begin{equation}\label{Q-nonDiag}
Q_{+}^{2L}=\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}=\sum_{i=1}^{N-1}2\Delta_{i}B_{i}^{2L-1}
\end{equation}
where, for the sake of notation we denoted $\Delta_{i}=(\alpha_{i}-\beta_{i})$. Therefore we can write 
\begin{equation}
Q^{2L}=Q^{2L}_{0}+Q_{+}^{2L}
\end{equation}
Observe that $Q^{2L}$ and $Q^{2L}_{0}$ are isospectral. \\
%  It has the property that commute with the equilibrium Hamiltonian.

Consider the matrix $Q_{0}^{2L}$ defined in \eqref{Q0Exp}. All terms are diagonal except the last one. This last non-diagonal can be identified with the second Casimir of the $gl(N-1)$ subalgebra. We denote it by $\hat{C}_{2}^{N-1}$, i.e.

@@

Moreover, we denote its eigenvalues by $C_{2}^{N-1}$. Since the configuration space of the process is given by the tensor product of the first fundamental representation of $gl(N)$, we can decompose it in a direct sum of irreducible representation of $gl(N)$. As a consequence, the Bethe states (that belong to the configurations space) can be written as a direct sum of vectors, each of them belonging to an irreducible representation of $gl(N)$. On these irreducible vectors $\hat{C}_{2}^{N-1}$ acts diagonally with eigenvalues $C_{2}^{N-1}$ given in terms of shifted weights, i.e. 

@@

@@

\paragraph{Exchange relations between charges} Since, in general, the coefficients of the polynomial form of the elements of $U_{0}(x)$ and the charges do not commute, it is useful to find explicit exchange relations among them. Using \eqref{EX1}, \eqref{EX2}, \eqref{EX3}, \eqref{EX4},\eqref{EX5} and \eqref{EX6} we obtain:

@@

Since $T(x)=\sum_{a=0}^{2L}Q^{2L}x^{a}$, the first non-diagonal charge $Q_{2L}$ commutes with $H^{''}$ and thus we can equivalently look for a matrix $W$ such that 

@@

where $\sigma_{0}^{tot}=e_{11}^{tot}-e_{22}^{tot}$ is the Pauli matrix. \\ 
In particular, by taking as equilibrium eigenvector in \eqref{Nice-W2} the vacuum state 

@@

Equation \eqref{Nice-W2} gives an explicit formula in term of the matrices $B_{1}^{2L-1}$ of the matrix $W$. We stress the fact that these closed formula for every non-equilibrium eigenvectors comes from the simple commutation relations between charges. We also notice that \eqref{Nice-W2} was found with other arguments also in \cite{frassek2020duality} and \cite{frassek2020eigenstates}, here we present a slightly different technique to obtain it. 

@@

Power expanding the matrix $W$ with respect to $\Delta_{1}=(\alpha_{1}-\beta_{1})$ we obtain 

@@

	\lim_{\epsilon\to 0}\epsilon\left((\Lambda_{m}+\epsilon)I-Q_{0}^{2L}\right)^{-1}|\Psi_{m}\rangle=\text{diag}\left\{0,\ldots,0,1,0,\ldots,0\right\}|\Psi_{m}\rangle

@@

		W=&\lim_{\epsilon\to 0}\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM\left(\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\}^{k_{1}},\ldots,\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}^{k_{N-1}}\right)

@@

In this case we do not have a closed formula for all non-equilibrium eigenvectors as in the case of $gl(2)$. Indeed, the exchange relation \eqref{ExQ0B-charges} has an extra creation operator

@@

This extra creation operator, mixes up the species different from $N$.  However, as we will show in subsection \ref{subsection-NONSS-W}, a closed formula for the non-equilibrium steady state can be written, since when acting on the vacuum the exchange relations do remain simple. 

@@

Performing a multi-variable power expansion of formula \eqref{WInCharges} with respect to $\Delta_{i} B_{i}^{2L-1}$ for all $i\in\{1,\ldots,N-1\}$  we obtain 
		W=&\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM_{k_{1},\ldots,k_{N-1}}\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\},\ldots,\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{N-1}^{2L-1}\right\}\right)
		\left(\Lambda_{\bm{m}}+\epsilon-Q_{0}^{2L}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
Observing that 

@@

we finally obtain \eqref{W-charges-Bad}. 

@@

Using \eqref{W-charges-Bad}, it is possible to find an explicit expression of the steady state $|\Psi^{''}\rangle$ of $H^{''}$ when $N>2$ by acting with $W$ on the vacuum state of the Hamiltonian $H_{0}$, i.e. 

@@

\textbf{Proof of \eqref{BActionVoid}: } using \eqref{B-charge} we have that 
\begin{align}
	B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=&2 \left(e_{iN}^{tot}e_{NN}^{tot}-\sum_{a,b=1\,:\,a<b}^{L}\sum_{k=1}^{N}e_{kN}^{[a]}e_{jk}^{[b]}\right)|\Psi_{0}^{0}\rangle\nonumber
	\\=&
	2\left(e_{iN}^{tot}e_{NN}^{tot}-\sum_{a,b=1\,:\,a<b}^{L}e_{NN}^{[a]}e_{jN}^{[b]}\right)|\Psi_{0}^{0}\rangle\nonumber\\=&
	\sum_{x=1}^{L}2L|N,\ldots,\tau_{x}=i,\ldots,N\rangle -2\sum_{x=1}^{L}(x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle
\end{align}
where we used the fact that 
\begin{equation}\label{eNN-action}
	 e_{NN}^{tot}|\Psi_{0}^{0}\rangle=L|\Psi_{0}^{0}\rangle
\end{equation}
\begin{flushright}
	$\square$
\end{flushright}
\item For all $i,j\in\{1,\ldots,N-1\}$ with $i\neq j$
\begin{equation}\label{Dij-ref}
	D_{i,j}^{2L}|\Psi_{0}^{0}\rangle=0
\end{equation}
The proof is trivial from the definition of \eqref{Dij-Charge}. 
\item For all $i,j\in\{1,\ldots,N-1\}$ with $i\neq j$ and for all $x\in\{1,\ldots,L\}$ 
\begin{equation}
	D_{i,j}^{2L}|N,\ldots,\tau_{x}=i,\ldots,N\rangle=-2|N,\ldots,\tau_{x}=j,\ldots,N\rangle
\end{equation}
The proof is trivial from \eqref{Dij-Charge}. 
\item For all $i,j\in\{1,\ldots,N-1\}$ with $i\neq j$ 
\begin{equation}\label{GoodRelation}
	D_{i,j}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=-2B_{j}^{2L-1}|\Psi_{0}^{0}\rangle
\end{equation}
\textbf{Proof of \eqref{GoodRelation}:}
\begin{align}
	D_{i,j}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle&= D_{j,i}\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle\nonumber
	\\&=
	-2e_{ji}^{tot}\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle\nonumber
	\\&=
	-4\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=j,\ldots,N\rangle\nonumber
	\\&=
	-2B_{j}|\Psi_{0}^{0}\rangle
\end{align}
\begin{flushright}
	$\square$
\end{flushright}
\item For all $k,j,i\in\{1,\ldots,N-1\}\;:\;k\neq i$
\begin{equation}\label{DijBk-different}
	D_{k,j}^{2L}B_{i}^{L}|\Psi_{0}^{0}\rangle=0
\end{equation}
The proof is trivial following the one of \eqref{GoodRelation}. 
\item For all $ \forall i\in \{1,\ldots,N-1\}$
\begin{equation}\label{Dii-ref}
	D_{i,i}^{2L}|\Psi_{0}^{0}\rangle=|\Psi_{0}^{0}\rangle\qquad D_{N,N}^{2L}|\Psi_{0}^{0}\rangle=(1+2L)|\Psi_{0}^{0}
\end{equation}
The proof is trivial using \eqref{Dii-charge} and \eqref{DNN-charge}. 
\item $Q_{0}^{2L}$ acts diagonally on the state $|\Psi_{0}^{0}\rangle$
\begin{equation}\label{Diagonal-Q-void}
	Q_{0}^{2L}|\Psi_{0}^{0}\rangle=(2L+N)(1+L)|\Psi_{0}^{0}\rangle
\end{equation}
\textbf{Proof of \eqref{Diagonal-Q-void}:}
\begin{align}
	Q_{0}^{2L}|\Psi_{0}^{0}\rangle&=\left((N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}\right)|\Psi_{0}^{0}\rangle\nonumber\\&=
	\left((N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}\right)|\Psi_{0}^{0}\rangle\nonumber
	\\&=
	(N-NL-2L+2(N+1)L+2L^{2})|\Psi_{0}^{0}\rangle
\end{align}
where we used the fact that 
\begin{equation}
	\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}|\Psi_{0}^{0}\rangle=0
\end{equation}
\begin{flushright}
	$\square$
\end{flushright}
\end{itemize}

@@

	Q_{0}^{2L}B_{j}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=B_{i}^{2L-1}B_{j}^{2L-1}\prod_{j=}^{2}\left(Q_{0}^{2L}-2j(D_{11}^{2L}+D_{NN}^{2L})+4j(j-1)\right)|\Psi_{0}^{0}\rangle

@@

	B_{j}^{2L-1}B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{j,j}^{2L}+2D_{N,N}^{2L}+8)\right)\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle\nonumber
	B_{j}^{2L-1}B_{i}^{2L-1}\left(Q_{0}^{2L}-4(D_{1,1}^{2L}+D_{N,N}^{2L}+8)\right)\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle

@@

it is also true. This can be shown by applying repeatedly \eqref{Two-Relation}.

>>>>

\paragraph{Proof of formula \eqref{exactCorrelations}} Consider $m$ particles of non-empty types $s_{i}\in\{1,\ldots,N-1\}$ in positions $y_{i}\in\{1,\ldots,L\}$ such that $y_{i}<y_{i+1}$ for all $i=1,\ldots,m$. We aim to compute the non-equilibrium stationary state correlation $\langle n_{s_{1}}^{y_{1}}\cdots n_{s_{m}}^{y_{m}} \rangle_{stat}$. By using duality, we showed in \eqref{CorrelationByABS-prob} that

@@

The two points correlations with respect to the non equilibrium distribution of the occupation variable of the species $s_{1},s_{2}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ with $x_{1}< x_{2}$ reads 

@@

Therefore, we compute the second cumulant, i.e. the two-point connected correlation

@@

The three points correlations with respect to the non equilibrium distribution of the occupation variable of the species $s_{1},s_{2},s_{3}\in \{1,\ldots,N-1\}$ at coordinates $y_{1},y_{2},y_{3}\in \{1,\ldots,L\}$ such that $y_{1}<y_{2}<y_{3}$

@@

Therefore, we compute the third cumulant, i.e. the three-point connected correlation as 

@@

As a consequence, using this sequence of transformations we can find all the eigenvectors of $H$ from the ones of $H_{0}$. Moreover, this allows to retrieve the steady state of $H$, by applying the sequence of transformation to the vacuum state of $H_{0}$, i.e. a state where all the sites are empty. This last transformation $W$ is non-local and to be constructed requires a joint work of perturbation theory and integrability, via the Quantum Inverse Scattering Method (QISM). 

@@

The matrices $R_{a,b}(x)$, $K_{a}(x)$ and $\widehat{K}_{a}(x)$ satisfy:

@@

	M_{0}(x)=R_{01}(x)\ldots R_{0L}(x)\qquad \widehat{M}_{0}(x)=R_{0L}(x)\ldots R_{01}(x)
$U_{0}(x)$ satisfies the following relation

@@

Using the matrix form of $U_{0}(x)$ \eqref{matrixForm-U}, the transfer matrix $T(x)$ reads

@@

Arguing similarly, we also write the elements of $U_{0}(x)$ as polynomials in $x$ 

@@

We will need the charge expansion of $T(x)$. As it will be clear in the following, only the first three conserved charges of the systems. As a consequence, we will compute only the first three coefficients for the diagonal elements of $U_{0}(x)$ and only the first one for the non-diagonal elements of $U_{0}(x)$ will be needed. Therefore, using \eqref{RURU}, we compute: 

@@

\item For $D_{i,j}(x)$ with $i,j=2,\ldots,N$ such that $i\neq j$
\begin{equation}\label{Dij-Charge}
D_{i,j}^{2L}=-2e_{ji}^{tot}
\end{equation}
\end{itemize}
\textbf{Remark}: when restricted to the case of $N=2$ species, we obtain equations (2.24)-(2.30) of \cite{frassek2020eigenstates}. \\ \\
Using these polynomial expansions we write the first three conserved charges of the system

\begin{align}
Q^{2L+2}&=D_{N,N}^{2L+1}-\sum_{i=1}^{N-1}D_{ii}^{2L+1}=N
\end{align}
\begin{align}
Q^{2L+1}&=ND_{N,N}^{2L+1}+D_{N,N}^{2L}-\sum_{i=1}^{N-1}D_{ii}^{2L}=N+2L-1
\end{align}
\begin{align}
Q^{2L\phantom{+}}&=ND_{N,N}^{2L}+D_{N,N}^{2L-1}-\sum_{i=1}^{N-1}D_{ii}^{2L-1}+\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
\end{align}
The charges $Q^{2L+2}$ and $Q^{2L+1}$ are proportional to the identity matrix, while $Q^{2L}$ contains non diagonal matrices and the boundary parameters $\alpha_{i},\beta_{i}$ $\forall i=1,\ldots,N-1$.\\
By construction it follows that 
\begin{equation}
\left[Q^{2L},H^{''}\right]=Q^{2L}H^{''}-H^{''}Q^{2L}=0
\end{equation}
while the commutation with the Hamiltonian $H^{''}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. We introduce the following matrix:
\begin{equation}
Q^{2L}_{0}:=ND_{N,N}^{2L}+D_{N,N}^{2L-1}-\sum_{i=1}^{N-1}D_{ii}^{2L-1}
\end{equation}
that is, using the coefficients previously computed, 
\begin{equation}\label{Q0Exp}
\begin{split}
Q^{2L}_{0}=(N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}
\end{split}
\end{equation}
We also introduce 
\begin{equation}\label{Q-nonDiag}
Q_{+}^{2L}=\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}=\sum_{i=1}^{N-1}2\Delta_{i}B_{i}^{2L-1}
\end{equation}
where, for the sake of notation we have denoted $\Delta_{i}=(\alpha_{i}-\beta_{i})$. Therefore we write 
\begin{equation}
Q^{2L}=Q^{2L}_{0}+Q_{+}^{2L}
\end{equation}
Observe that $Q^{2L}$ and $Q^{2L}_{0}$ are isospectral. \\
%  It has the property that commute with the equilibrium Hamiltonian.

Consider the matrix $Q_{0}^{2L}$ defined in \eqref{Q0Exp}. All terms are diagonal except the last one. This last non-diagonal term can be identified with the second Casimir of the $gl(N-1)$ subalgebra. We denote it by $\hat{C}_{2}^{N-1}$, i.e.

@@

Moreover, we denote its eigenvalues by $C_{2}^{N-1}$. Since the configuration space of the process is given by the tensor product of the first fundamental representation of $gl(N)$, we can decompose it in a direct sum of irreducible representation of $gl(N)$ (branching rule). As a consequence, the Bethe states (that belong to the configurations space) can be written as a direct sum of vectors, each of them belonging to an irreducible representation of $gl(N)$. On each of these irreducible vectors $\hat{C}_{2}^{N-1}$ acts diagonally with eigenvalues $C_{2}^{N-1}$ as 

@@

 where we introduce the shifted weights

@@

\paragraph{Exchange relations between charges} It is useful to find explicit exchange relations among the coefficients of the polynomial form of the elements of the matrix $U_{0}(x)$ defined in \eqref{matrixForm-U}. Using relations \eqref{EX1}-\eqref{EX6} we obtain:

@@

Since $T(x)=\sum_{a=0}^{2L}Q^{2L}x^{a}$, the first non-diagonal charge $Q^{2L}$ commutes with $H^{''}$ and thus we can equivalently look for a matrix $W$ such that 

@@

where $\sigma_{0}^{tot}=e_{11}^{tot}-e_{22}^{tot}$ is the Pauli matrix and where $B_{1}^{2L-1}$ is given in \eqref{B-charge}. In particular, by taking as equilibrium eigenvector in \eqref{Nice-W2} the vacuum state 

@@

Equation \eqref{Nice-W2} gives an explicit formula in term of the $B_{1}^{2L-1}$ of the matrix $W$. We stress the fact that these closed formula for every non-equilibrium eigenvectors comes from the simple commutation relations between charges. We also notice that \eqref{Nice-W2} was found with other arguments also in \cite{frassek2020duality} and \cite{frassek2020eigenstates}, here we present a slightly different technique to obtain it. 

@@

Power expanding the matrix $W$ using \eqref{veryUsefulSeries} and denoting $\Delta_{1}=(\alpha_{1}-\beta_{1})$ we obtain 

@@

	\lim_{\epsilon\to 0}\epsilon\left((\Lambda_{m}+\epsilon)I-Q_{0}^{2L}\right)^{-1}|\Psi_{m}^{0}\rangle=|\Psi_{m}^{0}\rangle

@@

		W=&\lim_{\epsilon\to 0}\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM_{k_{1},\ldots,k_{N-1}}\left(\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\},\ldots,\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}\right)

@@

In this case we do not have a closed formula for all non-equilibrium eigenvectors. Indeed, the exchange relation \eqref{ExQ0B-charges} has an extra creation operator

@@

This extra creation operator, mixes up the species different from $N$.  However, as we will show in subsection \ref{subsection-NONSS-W}, a closed formula for the non-equilibrium steady state can be written, since when acting on the vacuum the exchange relations do simplify. 

@@

Performing a multi-variable power expansion of formula \eqref{WInCharges} using \eqref{veryUsefulSeries} and denoting $\Delta_{i} B_{i}^{2L-1}$ for all $i\in\{1,\ldots,N-1\}$  we obtain 
		W=&\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM_{k_{1},\ldots,k_{N-1}}\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\},\ldots,\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{N-1}^{2L-1}\right\}\right)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|
where we used the fact that 

@@

This implies \eqref{W-charges-Bad}. 

@@

Using \eqref{W-charges-Bad}, it is possible to find an explicit expression of the steady state $|\Psi^{''}\rangle$ of $H^{''}$ when $N>2$ by acting with $W$ on the vacuum state $|\Psi_{m}^{0}\rangle$ of the Hamiltonian $H_{0}$, defined as

@@

\textbf{Proof of \eqref{BActionVoid}: } using \eqref{B-charge} we have that 
\begin{align}
	B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=&2 \left(e_{iN}^{tot}e_{NN}^{tot}-\sum_{a,b=1\,:\,a<b}^{L}\sum_{k=1}^{N}e_{kN}^{[a]}e_{jk}^{[b]}\right)|\Psi_{0}^{0}\rangle\nonumber
	\\=&
	2\left(e_{iN}^{tot}e_{NN}^{tot}-\sum_{a,b=1\,:\,a<b}^{L}e_{NN}^{[a]}e_{jN}^{[b]}\right)|\Psi_{0}^{0}\rangle\nonumber\\=&
	\sum_{x=1}^{L}2L|N,\ldots,\tau_{x}=i,\ldots,N\rangle -2\sum_{x=1}^{L}(x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle
\end{align}
where we used the fact that 
\begin{equation}\label{eNN-action}
	 e_{NN}^{tot}|\Psi_{0}^{0}\rangle=L|\Psi_{0}^{0}\rangle
\end{equation}
\begin{flushright}
	$\square$
\end{flushright}
\item For all $i,j\in\{1,\ldots,N-1\}$ with $i\neq j$
\begin{equation}\label{Dij-ref}
	D_{i,j}^{2L}|\Psi_{0}^{0}\rangle=0
\end{equation}
The proof is trivial from the definition of \eqref{Dij-Charge}. 
\item For all $i,j\in\{1,\ldots,N-1\}$ with $i\neq j$ and for all $x\in\{1,\ldots,L\}$ 
\begin{equation}
	D_{i,j}^{2L}|N,\ldots,\tau_{x}=i,\ldots,N\rangle=-2|N,\ldots,\tau_{x}=j,\ldots,N\rangle
\end{equation}
The proof is trivial from \eqref{Dij-Charge}. 
\item For all $i,j\in\{1,\ldots,N-1\}$ with $i\neq j$ 
\begin{equation}\label{GoodRelation}
	D_{i,j}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=-2B_{j}^{2L-1}|\Psi_{0}^{0}\rangle
\end{equation}
\textbf{Proof of \eqref{GoodRelation}:}
\begin{align}
	D_{i,j}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle&= D_{j,i}\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle\nonumber
	\\&=
	-2e_{ji}^{tot}\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle\nonumber
	\\&=
	-2\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=j,\ldots,N\rangle\nonumber
	\\&=
	-2B_{j}|\Psi_{0}^{0}\rangle
\end{align}
\begin{flushright}
	$\square$
\end{flushright}
\item For all $k,j,i\in\{1,\ldots,N-1\}\;:\;k\neq i$
\begin{equation}\label{DijBk-different}
	D_{k,j}^{2L}B_{i}^{L}|\Psi_{0}^{0}\rangle=0
\end{equation}
The proof is trivial following the one of \eqref{GoodRelation}. 
\item For all $ \forall i\in \{1,\ldots,N-1\}$
\begin{equation}\label{Dii-ref}
	D_{i,i}^{2L}|\Psi_{0}^{0}\rangle=|\Psi_{0}^{0}\rangle\qquad D_{N,N}^{2L}|\Psi_{0}^{0}\rangle=(1+2L)|\Psi_{0}^{0}
\end{equation}
The proof is trivial using \eqref{Dii-charge} and \eqref{DNN-charge}. 
\item $Q_{0}^{2L}$ acts diagonally on the state $|\Psi_{0}^{0}\rangle$
\begin{equation}\label{Diagonal-Q-void}
	Q_{0}^{2L}|\Psi_{0}^{0}\rangle=(2L+N)(1+L)|\Psi_{0}^{0}\rangle
\end{equation}
\textbf{Proof of \eqref{Diagonal-Q-void}:}
\begin{align}
	Q_{0}^{2L}|\Psi_{0}^{0}\rangle&=\left((N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}\right)|\Psi_{0}^{0}\rangle\nonumber\\&=
	\left((N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}\right)|\Psi_{0}^{0}\rangle\nonumber
	\\&=
	(N-NL-2L+2(N+1)L+2L^{2})|\Psi_{0}^{0}\rangle
\end{align}
where we used the fact that 
\begin{equation}
	\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}|\Psi_{0}^{0}\rangle=0
\end{equation}
\begin{flushright}
	$\square$
\end{flushright}
\end{itemize}

@@

	Q_{0}^{2L}B_{j}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=B_{i}^{2L-1}B_{j}^{2L-1}\prod_{j=1}^{2}\left(Q_{0}^{2L}-2j(D_{11}^{2L}+D_{NN}^{2L})+4j(j-1)\right)|\Psi_{0}^{0}\rangle

@@

	B_{j}^{2L-1}B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{j,j}^{2L}+2D_{N,N}^{2L})+8\right)\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle\nonumber
	B_{j}^{2L-1}B_{i}^{2L-1}\left(Q_{0}^{2L}-4(D_{1,1}^{2L}+D_{N,N}^{2L})+8\right)\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle

@@

it is also true. This can be shown by aa straight forward computation applying repeatedly \eqref{Two-Relation}.
